\documentclass[letterpaper,11pt,usenames,dvipsnames]{article}
\usepackage{lmodern}
\usepackage{xcolor} % Load color package without additional options

% Define granite color
\definecolor{granite}{rgb}{0.15, 0.15, 0.15} % Adjust the RGB values for a granite-like appearance
\pagecolor{granite} % Set the page background color to granite
\color{white} % Set text color to white

% Other packages and document settings remain the same
\usepackage{enumitem}
\setlist[itemize]{label=\textbullet}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Enable link colors
    linkcolor=white, % Set link color to white (or another color)
    citecolor=white, % Set citation color
    filecolor=white, % Set file link color
    urlcolor=white   % Set URL color
}

\usepackage{fancyhdr}
\usepackage[normalem]{ulem}

% Modify fancyhdr settings
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margin adjustments
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{white}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \hspace{0.5em}\textbf{\textit{\small#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
% Document content remains the same


%----------HEADING----------

% In your document
\begin{center}
    \textbf{\Huge \scshape Daniele D'Agnelli} \\ \vspace{1pt}
\href{https://www.linkedin.com/in/dagnelli/}{linkedin.com/in/dagnelli}
 \\ 
    London, United Kingdom
\end{center}

%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{Senior Engagement Manager with 12+ years in Professional Services, leading high-impact digital transformations that drive revenue growth and cost efficiency. Experienced in delivering AI solutions for complex challenges across Manufacturing, Healthcare, Oil\&Gas, Telecom, and Financial Services sectors for global enterprises. Skilled in aligning cross-functional teams and collaborating with senior leadership on programs exceeding \$15M, consistently exceeding metrics in adoption, customer satisfaction (NPS), and operational efficiency. Known for building trust-based client relationships and adept at navigating ambiguity. Technically proficient with expertise in software engineering, solution architecture, cloud engineering, and advanced machine learning, including LLMs and Generative AI.}
    }
 \end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {C3 AI}{London, United Kingdom}
      {Senior Engagement Manager}{June 2024 -- Present}
      \begin{itemize}[leftmargin=0.15in, label={}]
        \item \small{Responsible for the rollout and adoption of an AI-enabled Predictive Maintenance application for a Swiss building materials manufacturer, spanning over 100 plants, 2,000+ end users, and a total contract value exceeding \$10M.}
      \end{itemize}
      \vspace{-1em} 
      \resumeItemListStart
        \resumeItem{Partnered with cross-functional teams, including Product and Sales, to craft value-driven use cases, translating them into technical and functional requirements, detailed specifications, and actionable project plans.}
        \resumeItem{Expanded relationships by identifying new use cases and incremental staffing needs.}
        \resumeItem{Defined scope, requirements, timelines, and success metrics for projects, emphasizing customer self-sufficiency on the platform.}
        \resumeItem{Led project governance activities, including project planning, weekly reviews, cross-functional meetings, and executive status reports, ensuring alignment and transparency throughout project lifecycles.}
        \resumeItem{Directed all implementation activities, supervising teams across Application Development, Data Integration, Data Science, QA, and DevOps to ensure timely and successful delivery.}
        \resumeItem{Established trusted advisor relationships with clients, tracking and mitigating risks to maintain high customer satisfaction (CSAT) consistently achieving NPS Score \textgreater70.}
        \resumeItem{Played a key role in recruiting and attracting top talent to build a strong, client-focused services team.}
      \resumeItemListEnd
      
\vspace{-1.5em} % Adjust this value as needed
    \resumeSubheading
      {}{}
      {Engagement Manager}{August 2021 -- May 2024}
            \begin{itemize}[leftmargin=0.15in, label={}]
        \item \small{Led strategic initiatives across all Business Units and Partners, managing program with a \$15M budget and reporting directly to the VP of Customer Services.}
      \end{itemize}
      \vspace{0.2em} 


    \resumeSubheading
      {Deloitte}{London, United Kingdom}
      {Manager}{October 2018 -- July 2021}
      \begin{itemize}[leftmargin=0.15in, label={}]
        \item \small{Grew Deloitte UK's Anaplan practice from inception to 25+ practitioners, leading the first enterprise-wide deployment for a large British telco.}
      \end{itemize}

    \resumeSubheading
      {Accenture}{London, United Kingdom}
      {Management Consultant}{April 2017 -- September 2018}
      \vspace{0.2em} 


    \resumeSubheading
  {Codec}{Dublin, Ireland}
  {Consultant}{January 2015 -- March 2017}
        \vspace{0.2em} 


\resumeSubheading
  {Accenture}{Milan, Italy}
  {Software Engineer}{April 2012 -- December 2014}

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Abertay University}{Dundee, UK}
      {MSc Ethical Hacking and Cybersecurity (Distinction)}{2021 -- 2023}

    \resumeSubheading
      {University of Bari Aldo Moro}{Bari, Italy}
      {BSc Computer Science}{2005 -- 2011}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Certifications}{: Prince2 Practitioner} \\
     \textbf{Languages}{: Fluent in English and Italian (native)}
    }}
 \end{itemize}



\end{document}
